{\bf Systematic Testing of Concurrent C0 with Landslide}

### 2015-06-25 fp/paper.tex
fp: write about test case design

@@

evaluating stuff here

@@

>>>>

As always, the feasibility of a systematic test depends not just on the set of preemption points, but by the length and branch factor of the input test program (``test case'') used to drive the execution.
Even though we use Iterative Deepening, a new technique under development for automatically choosing feasible PPs, a test case's stress factor itself needs to be considered so that even a minimal state space can be within range for iterative deepening to expand upon.

{\bf Configuring test parameters.}
In C0, this is an especially sensitive issue, since many individual program statements involving channels can spawn a new thread, increasing not only the program length (in terms of number of concurrency events) but also the branch factor at the same time.
We chose the three test programs {\tt odd\_even\_sort4.c1}, {\tt seg.c1}, and {\tt bitstring1.c1}, and configured (by manual trial-and-error and with the help of Landslide's state space estimator) input parameters that would produce appropriately-sized state spaces.
The test case source code, including the parameters we settled on, are shown in Appendix~\ref{sec:codez}. For the case of {\tt bitstring1.c1}, we tested 3 separate configurations, with the values 1, 2, and 4 for {\tt COUNT}.
We abbreviate these test case names as OES, seg, BS(1), BS(2), and BS(4) respectively..

\newcommand\clis{\texttt{cs()}}
\newcommand\clir{\texttt{cr()}}
\newcommand\pros{\texttt{ps()}}
\newcommand\pror{\texttt{pr()}}
\newcommand\fwd{\texttt{fwd()}}
\newcommand\all{\texttt{ALL}}
{\bf Whitelisting functions.}
Landslide provides a feature to ``focus'' preemption points on specific sub-modules using the commands {\tt within\_function} and {\tt without\_function} (described in \cite{landslide}).
We found that, even limiting the stress factor of the above test cases to reasonable ``mid-range'' numbers, the state spaces could be too unwieldy, forcing us to fall back to minimal, often degenerate, parameters (i.e., making a bitstring incremet loop only go around 1 time would miss covering lots of program logic) if we wanted to achieve 100\% completion to verify the absence of bugs.
However, we found that using Landslide's whitelist/blacklist commands to further limit PPs to subsets of C0's concurrency implementation produced easily manageable state spaces.
This optimization allows us to more thoroughly verify each function alone, at the expense of more thorough testing of interleavings among 2 or more of each function.

The C0 concurrency runtime features five functions of interest for concurrency testing. These are
\texttt{client\_send\_msg()},
\texttt{client\_recv\_msg()},
\texttt{provider\_send\_msg()},
\texttt{provider\_recv\_msg()},
and
\texttt{forward()}.
We chose to run our evaluation with six possible test configurations; five where each of these functions is whitelisted alone in turn, which we'll abbreviate respectively as \clis, \clir, \pros, \pror, and \fwd; and one where all functions are whitelisted together, denoted \all.

@@

TODO

@@

TODO
